 

### 2021-01-20 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

@@

With increasing temperature experienced by foliage, photosynthesis and respiration are coupled at different rates upto photosynthetic thermal optimum. Beyond this inflection point, fluxnet global data analysis shows that photosynthesis declines whereas respiration increases exponentially, therefore, moving from carbon sink to carbon source with increasing temperature, independent of water and irradiance [Duffy et al.2021]

>>>>

![rough figure 1., needs some suggestions and info to include.] (https://github.com/EcoClimLab/vertical-thermal-review/blob/master/schematic/vertical%20thermal%20sensitivity%20image.png)

@@

With temperature increase, foliage photosynthesis and respiration are coupled at different rates upto photosynthetic thermal optimum. Beyond this inflection point, fluxnet global data analysis shows that photosynthesis declines whereas respiration increases exponentially, therefore, moving from carbon sink to carbon source with increasing temperature, independent of water and irradiance [Duffy et al.2021]
